{\fontfamily{ptm}\selectfont A Parameter Free Accelerated Proximal Gradient Method Without Restarting }

### 2025-01-16 Notebook LaTEX/R-WAPG/paper3.tex
>w<, changes done

\begin{abstract} 
    \noindent
    We analyze the accelerated proximal gradient method where the sequence that controls the momentum term is much weaker than the Nesterov's rule. 
    Our setting is the convex optimization problem $F^* = \min_x\{f(x) + g(x)\}$ where $f$ is $L$ Lipschitz smooth and $\mu\ge 0$ strongly convex and $g$ is closed and convex. 
    A much weaker condition of extrapolation parameters in $y_{k + 1} = x_{k + 1} - \theta_k(x_{k + 1} - x_k)$ is precisely characterized to show an upper bound on the optimality gap $F(x_k) - F^*$ using a generic algorithm R-WAPG (Relaxed Weak Accelerated Proximal Gradient) we proposed. 
    R-WAPG is a generic algorithm that has a has one convergence claim that unifies the convex and strongy convex cases. 
    R-WAPG can describes major Euclidean variants of the FISTA. 
    We showed convergence results for several notable variants of FISTA found in the literatures. 
    Inspired by a small detail in the proof, explorative numerical experiments were conducted to show the convergence of R-WAPG where the extrapolation sequence is generated using Bregman Divergence of $f$ on sucessive iterate $y_{k + 1}, y_{k}$.

\end{abstract}

@@

    \begin{definition}[Relaxed weak accelerated proximal gradient (R-WAPG)]\label{def:wapg}\;\\
        Choose any $x_1 \in \RR^n, v_1 \in \RR^n$. 
        Let $(\alpha_k)_{k \ge0}, (\rho_k)_{k \ge 0}$ be given by Definition \ref{def:rwapg-seq}. 
        The algorithm generates a sequence of vector $(y_k, x_{k + 1}, v_{k + 1})_{k \ge 1}$ for $k\ge 1$ by the procedures:  
        \begin{tcolorbox}
            For $k=1, 2, 3, \cdots$
            \begin{align*}
                \gamma_k &:= \rho_{k -1}L\alpha_{k - 1}^2, 
                \\
                \hat \gamma_{k + 1} & := (1 - \alpha_k)\gamma_k + \mu \alpha_k = L\alpha_k^2, 
                \\
                y_k &= 
                (\gamma_k + \alpha_k \mu)^{-1}(\alpha_k \gamma_k v_k + \hat\gamma_{k + 1} x_k), 
                \\
                g_k &= \mathcal G_L y_k, 
                \\
                v_{k + 1} &= 
                \hat\gamma^{-1}_{k + 1}
                (\gamma_k(1 - \alpha_k) v_k - \alpha_k g_k + \mu \alpha_k y_k), 
                \\
                x_{k + 1} &= T_L y_k. 
            \end{align*}    
        \end{tcolorbox}
    \end{definition}
    \begin{observation}\label{obs:r-wapg-observation-2}
        Observe that if $\rho_k = 1$ for all $k\ge 0$, then the above algorithm is similar to (2.2.7) in Nesterov's book \cite{nesterov_lectures_2018} because $L\alpha_k^{2} = (1 - \alpha_k)L\alpha_{k - 1}^2 + \mu \alpha_k$. 
        \par
        For all $k \ge 1$, the algorithm chains together the sequence of $(\hat \gamma_{k+1})_{k \ge 1}$ and $(\gamma_k)_{k \ge 1}$ in Definition \ref{prop:stepwise-lyapunov} through the equalities: 
        \begin{align*}
            \hat \gamma_{k + 1} 
            &= L\alpha_k^2 
            \\
            &= (1 - \alpha_k)\gamma_k + \alpha_k \mu
            \\
            &= (1 - \alpha_k)L\rho_{k - 1}\alpha_{k - 1}^2 + \alpha_k \mu
            \\
            &= (1 - \alpha_k)\rho_{k - 1}\hat \gamma_{k} + \alpha_k \mu. 
        \end{align*}
        The third equality from Observation \ref{obs:r-wapg-observation-1}. 
    \end{observation}
    Here is the main result of this section. 
    \begin{proposition}[R-WAPG convergence claim]\label{prop:wagp-convergence}\; \\
        Fix any arbitrary $x^* \in \RR^n, N \in \mathbb N$. 
        Let vector sequence $(y_k, v_{k}, x_{k})_{k \ge 1}$ and R-WAPG sequences $\alpha_k, \rho_k$ be given by Definition \ref{def:wapg}. 
        Define $R_1 = 0$ and suppose that for $k = 1, 2, \ldots, N$, we have $R_k$ recursively given by: 
        \begin{align*}
            R_{k + 1}
            := 
            \frac{1}{2}\left(
                L^{-1} - \frac{\alpha_k^2}{\hat \gamma_{k + 1}}
            \right)\Vert g_k\Vert^2
            + 
            (1 - \alpha_k)
            \left(
                \epsilon_k + R_k + 
                \frac{\mu\alpha_k\gamma_k}{2\hat \gamma_{k + 1}}
                \Vert v_k - y_k\Vert^2
            \right). 
        \end{align*}
        Then for all $k = 1, 2, \ldots, N$: 
        \begin{align*}
            & F(x_{k + 1}) - F(x^*) + \frac{L \alpha_k^2}{2}\Vert v_{k + 1} - x^*\Vert^2
            \\
            &\le 
            \left(
                \prod_{i = 0}^{k - 1} \max(1, \rho_{k})
            \right)
            \left(
                \prod_{i = 1}^{k} \left(1  - \alpha_i\right)
            \right)
            \left(
                F(x_1) - F(x^*) + \frac{L\alpha_0^2}{2}\Vert v_1 - x^*\Vert^2
            \right). 
        \end{align*}
    \end{proposition}

@@

        for all $k \ge 1$, $R_k$ satisfies \eqref{eqn:stepwise-lya-1}, hence unroll recursively using Proposition \ref{prop:stepwise-lyapunov}: 

@@

@@

\section{R-WAPG verifies existing accelerations scheme}\label{sec:rwapg-literatures}
    In addition to various equivalent forms of the R-WAPG algorithm, the R-WAPG sequences are much more flexible. 
    They generalize many existing sequences used in accelerated proximal gradient schemes. 
    \par
    This section demonstrates that several variants of FISTA in the literatures reduces to the R-WAPG method by setting up the R-WAPG sequences with additional assumptions. 
    This section will also demonstrate that the convergence claim (Proposition \ref{prop:wagp-convergence}) holds, and it derives convergence rates consistent with results in the literatures.  
    \begin{lemma}[R-WAPG sequences as inverted FISTA sequence]\label{lemma:inverted-fista-seq}
        Let R-WAPG sequence $(\rho_k)_{k \ge 0}, (\alpha_k)_{k \ge 0}$ given by Definition \ref{def:rwapg-seq}. 
        If $\mu = 0, \rho_k \ge 1\; \forall k \ge 0$, and $\alpha_0 = 1$, then: 
        \begin{enumerate}
            \item $\alpha_k^{-2} \ge \alpha_{k + 1}^{-2} - \alpha_{k + 1}^{-1}\; \forall k \ge 0$
            \item Let $t_k := \alpha_k^{-1}$, then $0 < t_{k + 1} \le (1/2)\left(1 + \sqrt{1 + 4t_k^2}\right)\;\forall k\ge 0$, hence the name: ``Inverted FISTA sequence''. 
            \item $\prod_{i = 1}^k\max(1, \rho_{k - 1})(1 - \alpha_k) = \alpha_k^2 \quad (\forall k \ge 1)$. 
        \end{enumerate}
    \end{lemma}
    \begin{proof}
        We start proving (i). 
        For all $k \ge 1$: 
        \begin{align*}
            \alpha_{k + 1}^2 
            &= (1 - \alpha_{k + 1})\rho_k\alpha_k^2 + (\mu/L) \alpha_k
            \\
            &= (1 - \alpha_{k + 1})\rho_k\alpha_k^2 & \mu = 0 \text{ assumed } 
            \\
            \implies 
            \alpha_{k + 1}^2 
            & \ge (1 - \alpha_{k + 1})\alpha_k^2 
            &  \rho_k \ge 1
            \\
            \iff 
            \alpha_k^{-2} 
            &\ge 
            \alpha_{k + 1}^{-2} - \alpha_{k + 1}^{-1}. 
        \end{align*}
        When $k = 0$, it has $\alpha_0 = 1$. 
        By definition of $\rho_0$ we have 
        \begin{align*}
            \alpha_1^2 &= 
            (1 - \alpha_1)\alpha_0^2\rho_0 \underset{\mu = 0}{=}
            \frac{\alpha_1^2}{\alpha_0^2(1 - \alpha_1)}(1 - \alpha_1)\alpha_0^2 = \alpha_1^2. 
        \end{align*}
        Therefore, (i) holds. 
        (i) is proved. 
        \par
        (i) $\implies$ (ii): Substituting $\alpha_k^{-1} = t_k$ changes (i) into $t_{k + 1}^2 - t_{k + 1} - t_{k}^2 \le 0$ for all $k \ge 0$. 
        Solving the equality yields $t_{k + 1} = (1/2)\left(1 \pm \sqrt{1 + 4 t_k^2}\right)$ for all $k \ge 0$. 
        Since $\alpha_k \in (0, 1)$, it means $t_k > 0$, hence the valid root is the larger root which gives the upper bound for $t_{k + 1}$ so: 
        \begin{align*}
            t_{k + 1} \in \left(
                0, \frac{1}{2}\left(1 + \sqrt{1 + 4t_k^2}\right) 
            \right]
        \end{align*}
        To prove (iii), because $\rho_k \ge 1$, we have $\prod_{i = 1}^{k} \max(1, \rho_{k - 1})(1 - 
        \alpha_k)= \prod_{i = 1}^{k}\rho_{k - 1}(1 - \alpha_k)$ for all $k \ge 1 $. 
        By definition $(\alpha_k)_{k \ge 1}, (\rho_k)_{k \ge 1}$ sequences they have for all $k \ge 1$: 
        \begin{align*}
            \alpha_k^2 &= \rho_{k - 1}(1 - \alpha_k)\alpha_{k - 1}^2
            \\
            \iff 
            \alpha_k^2/\alpha_{k - 1}^2 &= \rho_{k - 1}(1 - \alpha_k)
            \\
            \prod_{i = 1}^{k}\rho_{k - 1}(1 - \alpha_k)
            &= 
            \prod_{i = 1}^{k}\alpha_k^2 /\alpha_{k - 1}^2= \alpha_k^2/\alpha_0. 
        \end{align*}
        Because $\alpha_0 = 1$, (iii) is justified. 
    \end{proof}
    \begin{remark}
        The sequence $t_k$ is exactly the same as in Theorem 3.1 of Chambolle, Dossal \cite{chambolle_convergence_2015}. 
    \end{remark}

@@

    \begin{theorem}[Fixed momentum APG]\label{thm:fixed-momentum-fista}
        Assume $L > \mu > 0$, let a pair of constant R-WAPG sequence: $(\alpha_k)_{k \ge0}, (\rho_k)_{k \ge 0}$ be given by Lemma \ref{lemma:constant-rwapg-seq}.
        Define $q := \mu/L$ and for any fixed $r \in \left(\sqrt{q}, \sqrt{q^{-1}}\right)$, let $\alpha_k := \alpha = r \sqrt{q}$ be the constant R-WAPG sequence. 
        Consider the algorithm with a constant momentum specified by the following: 
        \begin{tcolorbox}
            Define $\theta = \left(1 - r^{-1}\sqrt{q}\right)(1 - r\sqrt{q})(1 - q)^{-1}$. 
            \\
            Initialize $y_1 = x_1$; for $k = 1, 2, \ldots, N$, update: 
            \begin{align*}
                &x_{k + 1} = y_k + L^{-1}\mathcal G_L y_k, 
                \\
                & y_{k + 1} = x_{k + 1} + \theta(x_{k + 1} - x_k). 
            \end{align*}
        \end{tcolorbox}
        Then the algorithm generates $(x_k)_{k \ge 1}$ such that $F(x) - F(x^*)$ convergences at a rate of $\mathcal O\left(\max(1 - r\sqrt{q}, 1 - r^{-1}\sqrt{q})^k\right)$. 
    \end{theorem}
    \begin{proof}
        The constant sequence $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ is a valid R-WAPG sequence by Lemma \ref{lemma:constant-rwapg-seq}. 
        The algorithm presented here is the same as the R-WAPG momentum form because the term $\theta$ from Lemma \ref{lemma:constant-rwapg-seq} matches up with Definition \ref{def:r-wapg-momentum-form}. 
        Therefore, by Proposition \ref{prop:wagp-convergence} we have: 
        \begin{align*}
            & F(x_{k + 1}) - F^* + \frac{L\alpha_k^2}{2}\Vert v_{k + 1} - x^*\Vert^2
            \\
            &= 
            F(x_{k + 1}) - F^* + \frac{L\alpha_k^2}{2}\Vert x_{k + 1}  - x^* + (\alpha^{-1} - 1)(x_{k + 1} - x_k)\Vert^2
            \\
            &\le 
            \left(
                \prod_{i = 0}^{k - 1} \max(1, \rho_{k})
            \right)
            \left(
                \prod_{i = 1}^{k} \left(1  - \alpha_i\right)
            \right)
            \left(
                F(x_1) - F(x^*) + \frac{L\alpha_0^2}{2}\Vert v_1 - x^*\Vert^2
            \right)
            \\
            &= \left(
                \prod_{i = 1}^{k - 1} \max(1, \rho)(1 - \alpha)
            \right)
            \left(
                F(x_1) - F(x^*) + \frac{L\alpha_0^2}{2}\Vert v_1 - x^*\Vert^2
            \right)
            \\
            &= \max(1 - r\sqrt{q}, 1 - r^{-1}\sqrt{q})^k
            \left(
                F(x_1) - F(x^*) + \frac{L\alpha_0^2}{2}\Vert x_1 - x^*\Vert^2
            \right). 
            & \text{Lemma \ref{lemma:constant-rwapg-seq} (v)}
        \end{align*}
        The equivalency between the momentum representation of R-WAPG (Definition \ref{def:r-wapg-momentum-form}) and the similar triangle representation (Definition \ref{def:r-wapg-st-form}) allows us to write $v_{k + 1} = x_{k + 1} + (\alpha^{-1} - 1)(x_{k + 1} - x_k)$. 
        By the initialization condition $v_1 = x_1$ specified in Proposition \ref{prop:r-wapg-momentum-repr}, we can write $v_1$ as $x_1$.

    \end{proof}
    \begin{remark}
        When $r = 1$, the algorithm described above is exactly the same as the V-FISTA algorithm specified in (10.7.7) of his book \cite{beck_first-order_2017}. 
    \end{remark}

@@

    This section introduces an algorithm of our creation inspired by the remark of Proposition \ref{prop:stepwise-lyapunov}. 
    Algorithm \ref{alg:free-rwapg} estimates the $\mu$ constant as the algorithm executes and pools the information using the Bregman Divergence of the smooth part function $f$. 

@@

        This section gives figures and visual for numerical experiments conducted using FR-WAPG algorithm (Algorithm \ref{alg:free-rwapg}), with other APG algorithms in the literatures: the V-FISTA, and M-FISTA algorithm described in Section (10.7.7, 10.7.6) by Beck \cite{beck_first-order_2017}. 

@@

            Consider the minimization problem of $\min_x \{F(x):= f(x) + 0\}$ where the objective function is given by: 

@@

                \min_x

@@

            The smooth part is $f =\frac{1}{2}\Vert Ax - b\Vert^2$ and the nonsmooth is $g = \lambda\Vert x\Vert_1$. 

@@

\section{Discussion}
    We do not claim a strictly better performance of FR-WAPG (Algorithm \ref{alg:free-rwapg}) compared to well-established variants of APGs in literatures. 
    Our numerical experiments are explorative and we hope to inspire. 
    The presented theories (Proposition \ref{prop:stepwise-lyapunov}, \ref{prop:wagp-convergence}) are our best attempts at making sense of what is happening, and we did it directly with elementary algebra. 
    In addition, we provided some helpful results on the equivalent representations of R-WAPG to illustrate the descriptive power of the R-WAPG framework. 
    Nonetheless, two things are clear from the numerical experiments. 
    FR-WAPG performs better than V-FISTA on the first hundreds of iterations, and it doesn't require prior knowledge on parameter $L, \mu$. 
    \par
    Our theories are somewhat relevant to FR-WAPG since it can partially describe an upper bound of the optimality gap with any sequence of $\alpha_k \in (0, 1)$. 
    Unfortunately, it is difficult to know the sequence $(\alpha_k)_{k \ge 0}$ without running the algorithm. 
    It would require knowledge about the trajectory taken for a specific initial guess, and the property of $D_f$, the Bregman Divergence of the smooth part. 
    We feel that the breakthrough in understanding may not come from elementary results.  
    \par 
    From a practical point of view, the numerical experiments show that in the beginning of the algorithm, the estimate for $\mu$ can be overestimated.
    This is partially explained by the remark of Proposition \ref{prop:stepwise-lyapunov}. 
    It also showed that the algorithm performs with mixed charactercteristics of M-FISTA and V-FISTA and it's just fascinating. 
    Finally, we observed that the convergence of gradient mapping $\mathcal G_L(y_k)$ becomes more difficult and the algorithm may not be able to terminate for certain objectives.

>>>>

\begin{abstract} 
    \noindent
    We study the accelerated proximal gradient method where the sequence that controls the momentum term doesn't follow the Nesterov's rule. 
    The paper proposed R-WAPG, a generic algorithm that unifies the convergence results for strongly convex and convex where the extrapolation constant is characterized by a sequence that is much weaker than the Nesterov's rule. 
    The R-WAPG framework is able to describe several notable Euclidean variants of FISTA and verify their convergence. 
    In addition we also proposed the convergence rate of strongly convex objective with a constant momentum term. 
    Inspired by a small detail in the proof, we give a formuatlion of R-WAPG that doesn't require any parameter without using the idea of restarting which we call ``Free R-WAPG". 
    Explorative numerical experiments were conducted to show its competitive convergence with numerical experiments. 
\end{abstract}

@@

    \begin{definition}[Relaxed weak accelerated proximal gradient (R-WAPG)]\label{def:wapg}\;\\
        Choose any $x_1 \in \RR^n, v_1 \in \RR^n$. 
        Let $(\alpha_k)_{k \ge0}, (\rho_k)_{k \ge 0}$ be given by Definition \ref{def:rwapg-seq}. 
        The algorithm generates a sequence of vector $(y_k, x_{k + 1}, v_{k + 1})_{k \ge 1}$ for $k\ge 1$ by the procedures:  
        \begin{tcolorbox}
            For $k=1, 2, 3, \cdots$
            \begin{align*}
                \gamma_k &:= \rho_{k -1}L\alpha_{k - 1}^2, 
                \\
                \hat \gamma_{k + 1} & := (1 - \alpha_k)\gamma_k + \mu \alpha_k = L\alpha_k^2, 
                \\
                y_k &= 
                (\gamma_k + \alpha_k \mu)^{-1}(\alpha_k \gamma_k v_k + \hat\gamma_{k + 1} x_k), 
                \\
                g_k &= \mathcal G_L y_k, 
                \\
                v_{k + 1} &= 
                \hat\gamma^{-1}_{k + 1}
                (\gamma_k(1 - \alpha_k) v_k - \alpha_k g_k + \mu \alpha_k y_k), 
                \\
                x_{k + 1} &= T_L y_k. 
            \end{align*}    
        \end{tcolorbox}
    \end{definition}
    \begin{observation}\label{obs:r-wapg-observation-2}
        Observe that if $\rho_k = 1$ for all $k\ge 0$, then the above algorithm is similar to (2.2.7) in Nesterov's book \cite{nesterov_lectures_2018} because $L\alpha_k^{2} = (1 - \alpha_k)L\alpha_{k - 1}^2 + \mu \alpha_k$. 
        \par
        For all $k \ge 1$, the algorithm chains together the sequence of $(\hat \gamma_{k+1})_{k \ge 1}$ and $(\gamma_k)_{k \ge 1}$ in Definition \ref{prop:stepwise-lyapunov} through the equalities: 
        \begin{align*}
            \hat \gamma_{k + 1} 
            &= L\alpha_k^2 
            \\
            &= (1 - \alpha_k)\gamma_k + \alpha_k \mu
            \\
            &= (1 - \alpha_k)L\rho_{k - 1}\alpha_{k - 1}^2 + \alpha_k \mu
            \\
            &= (1 - \alpha_k)\rho_{k - 1}\hat \gamma_{k} + \alpha_k \mu. 
        \end{align*}
        The third equality from Observation \ref{obs:r-wapg-observation-1}. 
    \end{observation}
    Here is the main result of this section. 
    \begin{proposition}[R-WAPG convergence claim]\label{prop:wagp-convergence}\; \\
        Fix any arbitrary $x^* \in \RR^n, N \in \mathbb N$. 
        Let vector sequence $(y_k, v_{k}, x_{k})_{k \ge 1}$ and R-WAPG sequences $\alpha_k, \rho_k$ be given by Definition \ref{def:wapg}. 
        Define $R_1 = 0$ and suppose that for $k = 1, 2, \ldots, N$, we have $R_k$ recursively given by: 
        \begin{align*}
            R_{k + 1}
            := 
            \frac{1}{2}\left(
                L^{-1} - \frac{\alpha_k^2}{\hat \gamma_{k + 1}}
            \right)\Vert g_k\Vert^2
            + 
            (1 - \alpha_k)
            \left(
                \epsilon_k + R_k + 
                \frac{\mu\alpha_k\gamma_k}{2\hat \gamma_{k + 1}}
                \Vert v_k - y_k\Vert^2
            \right). 
        \end{align*}
        Then for all $k = 1, 2, \ldots, N$: 
        \begin{align*}
            & F(x_{k + 1}) - F(x^*) + \frac{L \alpha_k^2}{2}\Vert v_{k + 1} - x^*\Vert^2
            \\
            &\le 
            \left(
                \prod_{i = 0}^{k - 1} \max(1, \rho_{i})
            \right)
            \left(
                \prod_{i = 1}^{k} \left(1  - \alpha_i\right)
            \right)
            \left(
                F(x_1) - F(x^*) + \frac{L\alpha_0^2}{2}\Vert v_1 - x^*\Vert^2
            \right). 
        \end{align*}
    \end{proposition}

@@

        For all $k \ge 1$, $R_k$ satisfies \eqref{eqn:stepwise-lya-1}, hence unroll recursively using Proposition \ref{prop:stepwise-lyapunov}: 

@@

                \prod_{i = 0}^{k - 1} \max(1, \rho_{i})

@@

\section{R-WAPG verifies existing accelerations scheme}\label{sec:rwapg-literatures}
    In addition to various equivalent forms of the R-WAPG algorithm, the R-WAPG sequences are much more flexible. 
    They generalize many existing sequences used in accelerated proximal gradient schemes. 
    This section demonstrates that several variants of FISTA in the literatures reduces to the R-WAPG method by setting up the R-WAPG sequences with additional assumptions. 
    This section will also demonstrate that the convergence claim (Proposition \ref{prop:wagp-convergence}) holds, and it derives convergence rates consistent with results in the literatures.  
    The table follows demonstrates the R-WAPG convergence results specialized into various settings. 
    \begin{table}[H]
        {\scriptsize
        \begin{tabular}{|l|l|l|l|l|}
        \hline
            Algorithm & $\mu$ & $\alpha_k$ & $\rho_k$ & Convergence of $F(x_k) - F^*$ 
        \\ \hline
            R-WAPG in Definition \ref{def:wapg} & 
            $\mu \ge 0$ &
            $\alpha_k \in(\mu/L, 1)$ & 
            $\rho_k > 0$ &  
            \begin{tabular}{l}
                $\mathcal O \left(\prod_{i = 0}^{k-1} \max(1, \rho_i)(1 - \alpha_{i + 1})\right)$
                (Proposition \ref{prop:wagp-convergence})
            \end{tabular}
        \\ \hline
            Chambolle, Dossal 2015 \cite{chambolle_convergence_2015} &  
            $\mu = 0$  &
            $ 0< \alpha_k^{-2} \le \alpha_{k + 1}^{-1} - \alpha_{k + 1}^{-2}$ & 
            $\rho_k \ge 1$ &  
            \begin{tabular}{l}
                $\mathcal O(\alpha_k^{2})$ \\ (Theorem \ref{thm:r-wapg-on-cham-doss})    
            \end{tabular}
        \\ \hline
            V-FISTA Beck (10.7.7) \cite{beck_first-order_2017} &
            $\mu > 0$&
            $\alpha_k = \sqrt{\mu/L}$ & 
            $\rho_k = 1$ &
            \begin{tabular}{l}
                $\mathcal O\left((1 - \sqrt{\mu/L})^k\right)$, 
                (Theorem \ref{thm:fixed-momentum-fista}, remark)
            \end{tabular}
        \\ \hline
            R-WAPG in Definition \ref{def:wapg} &  
            $\mu > 0$ &
            $\alpha_k = \alpha \in (\mu/L, 1)$ &  
            $\rho_k = \rho > 0$ & 
            \begin{tabular}{l}
                $\mathcal O \left(\max((1 - \alpha), 1 - \mu/(\alpha L))^{k} \right)$\\
                (Theorem \ref{thm:fixed-momentum-fista})
            \end{tabular}
        \\ \hline
        \end{tabular}
    \end{table}
    The lemma follows characterizes momentum sequences appears in the literatures using Definition \ref{def:rwapg-seq}. 
    \begin{lemma}[R-WAPG sequences as inverted FISTA sequence]\label{lemma:inverted-fista-seq}
        Let R-WAPG sequence $(\rho_k)_{k \ge 0}, (\alpha_k)_{k \ge 0}$ given by Definition \ref{def:rwapg-seq}. 
        If $\mu = 0, \rho_k \ge 1\; \forall k \ge 0$, and $\alpha_0 = 1$, then: 
            \item $\alpha_k^{-2} \ge \alpha_{k + 1}^{-2} - \alpha_{k + 1}^{-1}\; \forall k \ge 0$
            \item Let $t_k := \alpha_k^{-1}$, then $0 < t_{k + 1} \le (1/2)\left(1 + \sqrt{1 + 4t_k^2}\right)\;\forall k\ge 0$, hence the name: ``Inverted FISTA sequence''. 
            \item $\prod_{i = 1}^k\max(1, \rho_{k - 1})(1 - \alpha_k) = \alpha_k^2 \quad (\forall k \ge 1)$. 
        We start proving (i). 
        For all $k \ge 1$: 
            \alpha_{k + 1}^2 
            &= (1 - \alpha_{k + 1})\rho_k\alpha_k^2 + (\mu/L) \alpha_k
            &= (1 - \alpha_{k + 1})\rho_k\alpha_k^2 & \mu = 0 \text{ assumed } 
            \alpha_{k + 1}^2 
            & \ge (1 - \alpha_{k + 1})\alpha_k^2 
            &  \rho_k \ge 1
            \alpha_k^{-2} 
            \alpha_{k + 1}^{-2} - \alpha_{k + 1}^{-1}. 
        When $k = 0$, it has $\alpha_0 = 1$. 
        By definition of $\rho_0$ we have 
            \alpha_1^2 &= 
            (1 - \alpha_1)\alpha_0^2\rho_0 \underset{\mu = 0}{=}
            \frac{\alpha_1^2}{\alpha_0^2(1 - \alpha_1)}(1 - \alpha_1)\alpha_0^2 = \alpha_1^2. 
        Therefore, (i) holds. 
        (i) is proved. 
        (i) $\implies$ (ii): Substituting $\alpha_k^{-1} = t_k$ changes (i) into $t_{k + 1}^2 - t_{k + 1} - t_{k}^2 \le 0$ for all $k \ge 0$. 
        Solving the equality yields $t_{k + 1} = (1/2)\left(1 \pm \sqrt{1 + 4 t_k^2}\right)$ for all $k \ge 0$. 
        Since $\alpha_k \in (0, 1)$, it means $t_k > 0$, hence the valid root is the larger root which gives the upper bound for $t_{k + 1}$ so: 
            t_{k + 1} \in \left(
                0, \frac{1}{2}\left(1 + \sqrt{1 + 4t_k^2}\right) 
            \right]
        To prove (iii), because $\rho_k \ge 1$, we have $\prod_{i = 1}^{k} \max(1, \rho_{k - 1})(1 - 
        \alpha_k)= \prod_{i = 1}^{k}\rho_{k - 1}(1 - \alpha_k)$ for all $k \ge 1 $. 
        By definition $(\alpha_k)_{k \ge 1}, (\rho_k)_{k \ge 1}$ sequences they have for all $k \ge 1$: 
            \alpha_k^2 &= \rho_{k - 1}(1 - \alpha_k)\alpha_{k - 1}^2
            \alpha_k^2/\alpha_{k - 1}^2 &= \rho_{k - 1}(1 - \alpha_k)
            \prod_{i = 1}^{k}\rho_{k - 1}(1 - \alpha_k)
            \prod_{i = 1}^{k}\alpha_k^2 /\alpha_{k - 1}^2= \alpha_k^2/\alpha_0. 
        Because $\alpha_0 = 1$, (iii) is justified. 
        The sequence $t_k$ is exactly the same as in Theorem 3.1 of Chambolle, Dossal \cite{chambolle_convergence_2015}. 

@@

    \begin{theorem}[Fixed momentum APG]\label{thm:fixed-momentum-fista}
        Assume $L > \mu > 0$, let a pair of constant R-WAPG sequence: $(\alpha_k)_{k \ge0}, (\rho_k)_{k \ge 0}$ be given by Lemma \ref{lemma:constant-rwapg-seq}.
        Define $q := \mu/L$ and for any fixed $r \in \left(\sqrt{q}, \sqrt{q^{-1}}\right)$, let $\alpha_k := \alpha = r \sqrt{q}$ be the constant R-WAPG sequence. 
        Consider the algorithm with a constant momentum specified by the following: 
        \begin{tcolorbox}
            Define $\theta = \left(1 - r^{-1}\sqrt{q}\right)(1 - r\sqrt{q})(1 - q)^{-1}$. 
            \\
            Initialize $y_1 = x_1$; for $k = 1, 2, \ldots, N$, update: 
            \begin{align*}
                &x_{k + 1} = y_k + L^{-1}\mathcal G_L y_k, 
                \\
                & y_{k + 1} = x_{k + 1} + \theta(x_{k + 1} - x_k). 
            \end{align*}
        \end{tcolorbox}
        Then the algorithm generates $(x_k)_{k \ge 1}$ such that $F(x) - F(x^*)$ convergences at a rate of $\mathcal O\left(\max(1 - r\sqrt{q}, 1 - r^{-1}\sqrt{q})^k\right)$. 
    \end{theorem}
    \begin{proof}
        The constant sequence $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ is a valid R-WAPG sequence by Lemma \ref{lemma:constant-rwapg-seq}. 
        The algorithm presented here is the same as the R-WAPG momentum form because the term $\theta$ from Lemma \ref{lemma:constant-rwapg-seq} matches up with Definition \ref{def:r-wapg-momentum-form}. 
        Therefore, by Proposition \ref{prop:wagp-convergence} we have: 
        \begin{align*}
            & F(x_{k + 1}) - F^* + \frac{L\alpha_k^2}{2}\Vert v_{k + 1} - x^*\Vert^2
            \\
            &= 
            F(x_{k + 1}) - F^* + \frac{L\alpha_k^2}{2}\Vert x_{k + 1}  - x^* + (\alpha^{-1} - 1)(x_{k + 1} - x_k)\Vert^2
            \\
            &\le 
            \left(
                \prod_{i = 0}^{k - 1} \max(1, \rho_{k})
            \right)
            \left(
                \prod_{i = 1}^{k} \left(1  - \alpha_i\right)
            \right)
            \left(
                F(x_1) - F(x^*) + \frac{L\alpha_0^2}{2}\Vert v_1 - x^*\Vert^2
            \right)
            \\
            &= \left(
                \prod_{i = 1}^{k - 1} \max(1, \rho)(1 - \alpha)
            \right)
            \left(
                F(x_1) - F(x^*) + \frac{L\alpha_0^2}{2}\Vert v_1 - x^*\Vert^2
            \right)
            \\
            &= \max(1 - r\sqrt{q}, 1 - r^{-1}\sqrt{q})^k
            \left(
                F(x_1) - F(x^*) + \frac{L\alpha_0^2}{2}\Vert x_1 - x^*\Vert^2
            \right). 
            & \text{Lemma \ref{lemma:constant-rwapg-seq} (v)}
        \end{align*}
        The equivalency between the momentum representation of R-WAPG (Definition \ref{def:r-wapg-momentum-form}) and the similar triangle representation (Definition \ref{def:r-wapg-st-form}) allows us to write $v_{k + 1} = x_{k + 1} + (\alpha^{-1} - 1)(x_{k + 1} - x_k)$. 
        By the initialization condition $v_1 = x_1$ specified in Proposition \ref{prop:r-wapg-momentum-repr}, we can write $v_1$ as $x_1$. 
    \end{proof}
    \begin{remark}
        When $r = 1$, the algorithm described above is exactly the same as the V-FISTA algorithm specified in (10.7.7) of his book \cite{beck_first-order_2017}. 
    \end{remark}

@@

    In this section, we propose Algorithm \ref{alg:free-rwapg} which estimates the $\mu$ constant as the algorithm executes, and it pools the information using the Bregman Divergence of the smooth part function $f$. 
    It is called Free R-WAPG because it doesn't require any knowledge of $\mu, L$ in prior for the smooth part $f$, making it parameter-free. 

@@

        This section we conduct numerical experiments conducted using FR-WAPG algorithm (Algorithm \ref{alg:free-rwapg}), and compare with other APG algorithms in the literatures: the V-FISTA, and M-FISTA algorithm described in Section (10.7.7, 10.7.6) by Beck \cite{beck_first-order_2017}. 

@@

            Consider the minimization problem of $\min_{x \in \RR^n} \{F(x):= f(x) + 0\}$ where the objective function is given by: 

@@

                \min_{x \in \RR^n}

@@

            The smooth part is $f(x) =\frac{1}{2}\Vert Ax - b\Vert^2$ and the nonsmooth is $g(x) = \lambda\Vert x\Vert_1$. 

@@

\section{Discussion}
    This paper provides the results of an upper bound (Proposition \ref{prop:wagp-convergence}) on the optimality gap $F(x_k) - F^*$ for smooth plus nonsmooth composite optimization problem with convex objectives where under the much weaker assumption for the momentum parameter specified by Definition \ref{def:rwapg-seq}. 
    The proposed R-WAPG unifies the convergence proof for major Euclidean variants of FISTA with strong convexity parameter $\mu \ge 0$. 
    No analogous convergence framework had been identified yet in the literatures that proves the convergences of several variants (with and without strong convexity parameter) with momentum sequences that doesn't follow the Nesterov's rule. 
    \par
    In addition, we proposed explorative numerical experiments for Free R-WAPG (Algorithm \ref{alg:free-rwapg}) showcasing a parameter free algorithm that doesn't use the idea of restarting to achieve competitive convergence rate. 
    Unfortunately a precise description of the convergence rate of Free R-WAPG remains a mystery. 
    Our convergence framework gives an upper bound using the sequence $(\alpha_k)_{k \ge 0} \in (\mu/L, 1)$, but it requires knowing what the sequence would be in advanced given the initial conditions and the objective function. 
    \par
    From a practical perspective, Algorithm \ref{alg:free-rwapg} shows competitive results of convergence of strongly convex function.  
    The algorithm behaves in way having characteristics of both V-FISTA and M-FISTA which is fascinating. 
    In addition, of being parameter free, the algorithm works well with auto-differentiation framework because it requires the function value at the same point where the gradient is evaluated at $y_k$. 
    We do note that in the case when function is not strongly convex, the function value converges without $\Vert \mathcal G_L(y_k)\Vert$ converging.
